2040 greenhouse gas reduction targets and energy transitions in line with the EU Green Deal

### 2024-09-05 report_paperCharts.Rmd
small changes

g[["security of supply - net fossil with range"]] <- 
  ggplot(plotData,aes(x=period,y=value)) +
  geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = factor(period), alpha=factor(period))) +
  geom_errorbar(data=plotData %>% filter(period == 2040, scenario == mainScen), aes(ymin=ribbon.min, ymax=ribbon.max), width=4, colour="black", alpha=0.9, linewidth=1,position = position_dodge(width=2)) +
  # scale_y_continuous(labels = scales::percent, breaks = c(0,1,plotData[plotData$period == "2030",]$value,plotData[plotData$period == "2040",]$value,plotData[plotData$period == "2050",]$value)) +
  #coord_flip() +
  facet_wrap(~carrier,nrow=1) +
  theme_doubleColumn() +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank()) +
  scale_fill_manual(values = c("2020" = "black", "2030"= "black", "2040" = "#5a788b", "2050" = "black")) +
  scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
  theme(legend.position = "none") +
  labs(title = paste0("(b) Fossil energy carriers net imports (", unique(plotData$unit), ")")) #+ 
  #theme(plot.title = element_text(hjust = -0.4))

@@

@@

@@

@@

@@

@@

# Solar photovoltaics
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Cap|Electricity|Solar|PV") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Solar\nphotovoltaics") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

@@

# Carbon Capture and Storage 
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Carbon Management|Storage") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Carbon\nCapture and\nStorage") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

@@

@@

# Direct Electrification
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Final Energy|Electricity Share") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Electricity\nShare in\nFinal Energy") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

@@

# Carbon-free electricity share
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "SE|Electricity|carbon-free") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Carbon-free\nelectricity\nshare") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

@@

# Residual Fossil Emissions
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Residual\nFossil\nEmissions") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

@@

@@

@@

ggsave(paste0(outChartsFolder,"/svg/Figure 5. Milestones Panel.svg"), g[["milestone - hor targets"]] , device="svg", width = 12, height = 14, dpi=100, units = "in")
ggsave(paste0(outChartsFolder,"/png/Figure 5. Milestones Panel.png"), g[["milestone - hor targets"]] , device="png", width = 12, height = 14, dpi=300, units = "in")

>>>>

g[["security of supply - net fossil with range"]] <- 
  ggplot(plotData,aes(x=period,y=value)) +
  geom_col(data=plotData %>% filter(scenario == mainScen), aes(fill = factor(period), alpha=factor(period))) +
  geom_errorbar(data=plotData %>% filter(period == 2040, scenario == mainScen), aes(ymin=ribbon.min, ymax=ribbon.max), width=4, colour="black", alpha=0.9, linewidth=1,position = position_dodge(width=2)) +
  # scale_y_continuous(labels = scales::percent, breaks = c(0,1,plotData[plotData$period == "2030",]$value,plotData[plotData$period == "2040",]$value,plotData[plotData$period == "2050",]$value)) +
  #coord_flip() +
  facet_wrap(~carrier,nrow=1) +
  theme_doubleColumn() +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank()) +
  scale_fill_manual(values = c("2020" = "black", "2030"= "black", "2040" = "#5a788b", "2050" = "black")) +
  scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
  theme(legend.position = "none") +
  labs(title = paste0("(b) Fossil energy carriers’ net imports (", unique(plotData$unit), ")")) #+ 
  #theme(plot.title = element_text(hjust = -0.4))

@@

violin_scale <- 3 
violin_color = "#bbbbbb"
violin_boxPlotWidth <- 1.5

@@

g[["milestone - violin"]][["Emissions reductions"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
  geom_violin(fill="#bbbbbb", scale = violin_scale) + #, trim=FALSE
  #geom_errorbar(aes(ymin=min, ymax=max), width=1, colour="black", alpha=0.9, linewidth=0.5) +
  geom_boxplot(outlier.shape = NA, width=1.5) +
  geom_hline(yintercept=0.55, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 0.55, label = "FitFor55", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=reduction_h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = reduction_h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=0.8*geomText.size)

@@

g[["milestone - violin"]][["Energy savings"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mtoe/yr)")), aes(x = period, y = value, group=period)) +
  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
  geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 750, label = "REPowerEU", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  annotate("text", x = Inf, y = 787, label = "FitFor55", angle=90, vjust = 1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=h %>% filter(period==2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = h %>% filter(period==2022) %>% pull(value), label = "2022", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,400,1000)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(Mtoe/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)

@@

g[["milestone - violin"]][["Electricity Demand"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (TWh)")), aes(x = period, y = value, group=period)) +
  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -1, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,5000)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(TWh)", hjust = 1, color = "#666666", size = 0.8*geomText.size)

@@

g[["milestone - violin"]][["Renewables Share"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
  geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 0.4, label = "RED II revised", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 0.45, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = addHist$res %>% filter(type == "RES", period == 2022) %>% pull(value), label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size = 0.8*geomText.size)

@@

g[["milestone - violin"]][["Wind capacity"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (GW)")), aes(x = period, y = value, group=period)) +
  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
  geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 255, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  #scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,1000)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(GW)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
# Solar photovoltaics
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Cap|Electricity|Solar|PV") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Solar\nphotovoltaics") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

@@

g[["milestone - violin"]][["Solar photovoltaics"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (GW)")), aes(x = period, y = value, group=period)) +
  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
  geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 600, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 208.9, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,2500)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(GW)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
# Carbon Capture and Storage 
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Carbon Management|Storage") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Carbon\nCapture and\nStorage") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

@@

g[["milestone - violin"]][["Carbon Capture and Storage"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)")), aes(x = period, y = value, group=period)) +
  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
  geom_hline(yintercept=50, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = 50, label = "Net-Zero\nIndustry Act", angle=90, vjust = 0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,400)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) +
  theme(strip.clip = "off")#+
  #annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)

@@

g[["milestone - violin"]][["Novel CDR"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)")), aes(x = period, y = value, group=period)) +
  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,400)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)
# Direct Electrification
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Final Energy|Electricity Share") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Electricity\nShare in\nFinal Energy") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

@@

g[["milestone - violin"]][["Direct Electrification"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=geomText.size, size = 0.8*geomText.size)
# Carbon-free electricity share
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "SE|Electricity|carbon-free") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Carbon-free\nelectricity\nshare") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

@@

g[["milestone - violin"]][["Carbon-free electricity share"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (%)")), aes(x = period, y = value, group=period)) +
  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
  geom_hline(yintercept=h, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = Inf, y = h, label = "2022", angle=90, vjust = -0.5, hjust = 0, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(%)", hjust = 1, color = "#666666", size=geomText.size, size = 0.8*geomText.size)
# Residual Fossil Emissions
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Emi|CO2|Residual Fossil") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Residual\nFossil\nEmissions") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

@@

g[["milestone - violin"]][["Residual Fossil Emissions"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mt CO2/yr)")), aes(x = period, y = value, group=period)) +
  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,2500)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(Mt CO2/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)

@@

g[["milestone - violin"]][["Domestic Hydrogen Production"]] <- ggplot(plotData %>% mutate(target = paste0(gsub("\n", " ", target)," (Mtoe/yr)")), aes(x = period, y = value, group=period)) +
  geom_violin(fill=violin_color, scale = violin_scale)  + #, trim=FALSE
  #geom_errorbar(aes(ymin=min, ymax=max), width=6, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=violin_boxPlotWidth) +
  geom_hline(yintercept=10, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = -Inf, y = 10, label = "REPowerEU\ndomestic", angle=90, vjust = 0.5, hjust = 1, color = "black", alpha = 0.5, size = 0.8*geomText.size) +
  facet_grid(.~target, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_x_reverse(breaks=c(2030,2040), labels = c(2030,2040), minor_breaks = NULL) +
  expand_limits(y=c(0,20)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  theme(strip.placement = "outside") +
  #theme(axis.text.x = element_text(size = 1*theme.double.text.size)) +
  #theme(axis.text.y = element_text(size = 1*theme.double.text.size)) +
  theme(strip.text.x = element_text(hjust = 0, margin=margin(l=0, b=20))) #+
  #annotate("text", x = -Inf, y = -Inf, label = "(Mtoe/yr)", hjust = 1, color = "#666666", size = 0.8*geomText.size)

@@

g[["milestone - violin targets"]] <- gridExtra::arrangeGrob(
  g[["milestone - violin"]][["Emissions reductions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
  g[["milestone - violin"]][["Energy savings"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
  g[["milestone - violin"]][["Renewables Share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
  g[["milestone - violin"]][["Direct Electrification"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
  g[["milestone - violin"]][["Carbon-free electricity share"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
  g[["milestone - violin"]][["Domestic Hydrogen Production"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),

  g[["milestone - violin"]][["Electricity Demand"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
  g[["milestone - violin"]][["Wind capacity"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
  g[["milestone - violin"]][["Solar photovoltaics"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),

  g[["milestone - violin"]][["Residual Fossil Emissions"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
  g[["milestone - violin"]][["Carbon Capture and Storage"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),
  g[["milestone - violin"]][["Novel CDR"]] + theme(plot.margin=margin(l = 30, r = 10,t = 30)),

ggsave(paste0(outChartsFolder,"/svg/Figure 5. Milestones Panel.svg"), g[["milestone - violin targets"]] , device="svg", width = 12, height = 14, dpi=100, units = "in")
ggsave(paste0(outChartsFolder,"/png/Figure 5. Milestones Panel.png"), g[["milestone - violin targets"]] , device="png", width = 12, height = 14, dpi=300, units = "in")
